---
title: "Overview of Gameday"
author: "Dustin Johnson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview of Gameday}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

## Introduction to gameday

The gameday package enables you to stay up-to-date with your NHL needs without diverting your eyes from an R coding project. Check if your favourite NHL team is playing, or glance at the scores of the day to monitor your pool!

## Getting Started

All you need to to is load the package!

```{r}
library(gameday)
```

## Using gameday

#### gday()
Use the function `gday()` to find the times that your favourite hockey team is playing. For instance, I would like to know if the Vancouver Canucks are playing today:

```{r}
# Check if Canucks are playing today
gday() # default is set to today's date and 'Canucks'.
```

Perhaps I would like to know if the Nashville Predators played on November 22, 2014. This can easily be done by setting the team and date:

```{r}
# Did the Predators play on November 22, 2014
gday(team = "predators", date = "2014-11-22")
```

How easy!

#### score()
The `score()` function is self-explanitory, as the only input is `date`. It simply provides the scores of all teams that played (or are playing) on a given date. This means, your scores can be update in real time! Let's say I wanted to know the scores of all games played today:

```{r}
score()
```

Or perhaps, I would like to know the scores of all teams that played on November 22, 2014.

```{r}
score(date = "2014-11-22")
```

If the entries are black, either no games have been played or you are attempting to predict the future.

#### Winners of the Day

We can also determine the winners of the day with the help of the `dplyr` package and make a nice plot of our results with `ggplot2`. 

```{r}
suppressPackageStartupMessages(library(dplyr))
library(ggplot2)

win.dat <- score("2014-11-22") %>%
	mutate(winner = ifelse(home_score > away_score, as.character(home), as.character(away))) %>%
	mutate(diff = ifelse(home_score > away_score, home_score-away_score, away_score-home_score)) %>%
	mutate(winner = reorder(winner, diff)) %>%
	select(winner, diff) %>%
	ggplot(aes(diff, winner)) + geom_point(aes(colour = winner), size = 3) + 
	guides(col = guide_legend(reverse = TRUE))
win.dat

```	
	
Use the `gameday` package and stay up to date with your game-to-game needs.


